---
title: "KTH Research Metrics"
subtitle: "Example dashboard — kth-quarto extension"
brand: _brand.yml
format:
  kth-quarto-dashboard: default
---

```{r}
#| label: setup
#| include: false

library(dplyr)
library(ggplot2)
library(plotly)

# Synthetic annual publication data
pubs <- data.frame(
  year  = 2015:2024,
  total = c(198, 215, 231, 249, 263, 278, 295, 312, 328, 342),
  oa    = c( 45,  52,  63,  78,  91, 108, 132, 168, 201, 253)
)

# Synthetic department data
depts <- data.frame(
  Department   = c("Computer Science", "Electrical Eng.", "Mechanical Eng.",
                   "Mathematics", "Physics", "Chemical Eng.",
                   "Biotechnology", "Civil Eng.", "Industrial Eng.", "Architecture"),
  Publications = c(87, 74, 68, 55, 52, 48, 43, 39, 37, 31),
  Citations    = c(1842, 1367, 1204, 923, 889, 743, 698, 541, 489, 312),
  `Open Access` = c(72, 58, 49, 44, 41, 35, 33, 28, 24, 18),
  check.names  = FALSE
)
```

# Overview

## Row {height="160px"}

```{r}
#| content: valuebox
#| title: "Publications (2024)"
#| icon: journal-text
#| color: "#004791"
342
```

```{r}
#| content: valuebox
#| title: "Open access rate"
#| icon: unlock
#| color: "#3f824e"
"74%"
```

```{r}
#| content: valuebox
#| title: "Active researchers"
#| icon: people
#| color: "#036eb8"
127
```

```{r}
#| content: valuebox
#| title: "Growth vs 2023"
#| icon: arrow-up-circle
#| color: "#A65900"
"+14"
```
## Row {height="55%"}

### Publications {width="58%"}

```{r}
#| label: pub-chart
#| title: "Publications"

colors <- c("Total" = "#004791", "Open access" = "#3f824e")

plot_ly() |>
  add_trace(
    x = pubs$year, y = pubs$total,
    type = "scatter", mode = "lines+markers", name = "Total",
    line   = list(color = colors[["Total"]], width = 2),
    marker = list(color = colors[["Total"]], size = 7)
  ) |>
  add_trace(
    x = pubs$year, y = pubs$oa,
    type = "scatter", mode = "lines+markers", name = "Open access",
    line   = list(color = colors[["Open access"]], width = 2),
    marker = list(color = colors[["Open access"]], size = 7)
  ) |>
  layout(
    xaxis         = list(tickvals = 2015:2024, tickcolor = "#646464",
                         tickfont = list(color = "#646464")),
    yaxis         = list(side = "right", automargin = TRUE,
                         tickcolor = "#646464",
                         tickfont = list(color = "#646464")),
    legend        = list(orientation = "h", x = 0, y = -0.15),
    font          = list(family = "Figtree", color = "#212121"),
    paper_bgcolor = "rgba(0,0,0,0)",
    plot_bgcolor  = "rgba(0,0,0,0)",
    margin        = list(l = 0, r = 0, t = 10, b = 0)
  ) |>
  config(displayModeBar = FALSE)
```

### Publications by department {width="42%"}

```{r}
#| label: dept-table
#| title: "Publications by department"

knitr::kable(depts, format = "html") |>
  kableExtra::kable_styling(
    full_width       = TRUE,
    bootstrap_options = c("hover", "sm", "borderless")
  ) |>
  kableExtra::column_spec(3, bold = TRUE, color = "#004791") |>
  kableExtra::column_spec(4, color = "#3f824e")
```

## Row {height="25%"}

### {width="33%"}

::: callout-note
**2024 milestone:** Total publications exceeded 340 for the first time.
Open access now accounts for 74 % of output.
:::

### {width="33%"}

::: callout-tip
Use the **Style Guide** page to see how all callout types and typography
components are rendered with the kth-quarto theme.
:::

### {width="34%"}

::: callout-important
Figures for Q4 2024 are preliminary and subject to revision pending
final journal indexing.
:::

# Style Guide

## Row {height="50%"}

### Callout types {width="50%"}

The five Quarto callout types styled via `kth-content.css`:

::: callout-note
**Note** — `--bs-primary` border (`#004791`). Supplementary information,
definitions, or things the reader should be aware of.
:::

::: callout-tip
**Tip** — `--bs-success` border (`#3f824e`). Best practice suggestions,
shortcuts, or recommendations.
:::

::: callout-warning
**Warning** — KTH orange border (`#A65900`). Caveats or situations
where the reader should proceed with care.
:::

::: callout-caution
**Caution** — also orange. Use for potentially harmful or hard-to-reverse
actions.
:::

::: callout-important
**Important** — `--bs-danger` border (`#d8351e`). Critical information
the reader must not miss.
:::

### Typography & code {width="50%"}

#### Headings use KTH blue (`#004791`)

Set via `--bs-heading-color` in `kth-content.css`, overriding the
pre-compiled Bootswatch value.

##### Body text

Body uses `--bs-body-color: #212121` at `line-height: 1.6`.
Inline `code snippets` get a light grey background (`#ededed`) and
`0.9em` size — matching the `@kth/style` prose mixin spec.

The monospace font is **IBM Plex Mono** (embedded woff2):

```r
model <- lm(Citations ~ Publications, data = depts)
summary(model)$coefficients
```

## Row {height="50%"}

### Semantic colour reference {width="60%"}

| Role | CSS variable | Hex | Used in |
|---|---|---|---|
| Primary | `--bs-primary` | `#004791` | Buttons, value boxes |
| Success | `--bs-success` | `#3f824e` | Positive states, tips |
| Danger | `--bs-danger` | `#d8351e` | Errors, important callouts |
| Link | `--bs-link-color` | `#036eb8` | Hyperlinks |
| Body text | `--bs-body-color` | `#212121` | Default text |
| Headings | `--bs-heading-color` | `#004791` | h1–h6 |
| Code bg | — | `#ededed` | Inline code background |

### Value box colours {width="40%"}

::: {.valuebox icon="square-fill" color="#004791"}
primary
**#004791**
:::

::: {.valuebox icon="square-fill" color="#3f824e"}
success
**#3f824e**
:::

::: {.valuebox icon="square-fill" color="#d8351e"}
danger
**#d8351e**
:::
